Tables

### 2021-04-17 analysis/01_clean-generate-data.Rmd
Use targets now!

---
title: "Generate and clean simulated data"
author: "Suparna Chaudhry, Marc Dotson, and Andrew Heiss"
date: "Last run: `r format(Sys.time(), '%F')`"
output: 
  html_document:
    code_folding: show
    pandoc_args:
      - "--default-image-extension=png"
editor_options: 
  chunk_output_type: console
---

```{r load-packages, warning=FALSE, message=FALSE}
library(tidyverse)
library(fastDummies)
library(scales)
library(readxl)
library(here)

# Turn off grouping message
options(dplyr.summarise.inform = FALSE)

# Project-specific functions
source(here("R", "graphics.R"))

# General settings
source(here("analysis", "options.R"))

# Make all the randomness reproducible
set.seed(1234)
```

```{r simpler-excel-based-model, message=FALSE}
sim_raw <- read_excel(here("data", "raw_data", "Market Simulator Version 01.xlsx"),
                      sheet = "Results", range = "O3:AU27")

orgs_raw <- read_excel(here("data", "raw_data", "Market Simulator Version 01.xlsx"),
                       sheet = "Results", range = "N4:O27", 
                       col_names = c("organization", "org_details"))

orgs_clean <- orgs_raw %>% 
  separate(org_details, into = c("org_issue", "org_funding", "org_relationship"), sep = ", ")

personas_raw <- read_excel(here("data", "raw_data", "Market Simulator Version 01.xlsx"),
                           sheet = "Results", range = "P2:AU3") %>% 
  pivot_longer(everything(), names_to = "persona", values_to = "persona_details")

personas_clean <- personas_raw %>% 
  separate(persona_details, into = c("demographics", "actions", "persona_trust"), sep = ", ") %>% 
  separate(demographics, into = c("persona_income", "persona_gender"), sep = " Income ") %>% 
  separate(actions, into = c("persona_ideology", "persona_experience"), sep = " that ")

sim_long <- sim_raw %>% 
  rename(org_details = `...1`) %>% 
  pivot_longer(cols = -org_details, names_to = "persona_details", values_to = "share")

sim_excel_clean <- sim_long %>% 
  left_join(orgs_raw, by = "org_details") %>% 
  left_join(personas_raw, by = "persona_details") %>% 
  separate(org_details, into = c("org_issue", "org_funding", "org_relationship"), sep = ", ") %>% 
  separate(persona_details, into = c("demographics", "actions", "persona_trust"), sep = ", ") %>% 
  separate(demographics, into = c("persona_income", "persona_gender"), sep = " Income ") %>% 
  separate(actions, into = c("persona_ideology", "persona_experience"), sep = " that ") %>% 
  mutate(org_issue = recode(org_issue, "Refugess Relief" = "Refugee Relief"),
         org_funding = recode(org_funding, "Grants" = "Mostly funded by government grants",
                              "Small Donors" = "Mostly funded by small donors"),
         persona_income = paste(persona_income, "income"),
         persona_income = factor(persona_income, levels = c("Lower income", "Higher income"), ordered = TRUE),
         persona_trust = recode(persona_trust,
                                "Doesn't Trust or Donate" = "Less trusting; donates and volunteers less often",
                                "Trusts and Donates" = "More trusting; donates and volunteers often"),
         persona_experience = recode(persona_experience,
                                     "Doesn't Read or Travel" = "Doesn't follow news; has not travelled abroad",
                                     "Reads and Travels" = "Follows the news; has travelled abroad")) %>% 
  mutate_at(vars(organization, persona), ~fct_inorder(.))
```

```{r load-data, message=FALSE}
# Gammas of the "everything" model
gammas <- read_rds(
  here('data', 'raw_data', 'posterior_draws', 'public_political_social_charity_demo.rds')
  ) %>% 
  group_by(i, j) %>% 
  summarize(gamma_mean = mean(Gamma)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = j, values_from = gamma_mean) %>% 
  select(-i) %>% 
  t()
```

```{r possible-organizations}
organization_columns <- c("organization", "issue.area", "transparency", 
                          "accountability", "funding", "relationship")

organization_possibilities <- expand_grid(
  issue.area = c("Emergency response", "Environment", "Human rights", "Refugee relief"),
  relationship = c("Friendly", "Criticized", "Under crackdown"),
  funding = c("Small private donations", "Government grants")
) %>% 
  mutate(org_id = paste0("org", 1:n()))

organizations <- organization_possibilities %>% 
  mutate(
    organization = "Red Cross",
    transparency = "Yes",
    accountability = "Yes"
  ) %>% 
  select(org_id, all_of(organization_columns)) %>% 
  mutate(organization = factor(organization, 
                               levels = c("Amnesty International", "Greenpeace", 
                                          "Oxfam", "Red Cross")),
         issue.area = factor(issue.area, 
                            levels = c("Emergency response", "Environment", 
                                       "Human rights", "Refugee relief")),
         transparency = factor(transparency, levels = c("No", "Yes")),
         accountability = factor(accountability, levels = c("No", "Yes")),
         funding = factor(funding, levels = c("Small private donations", 
                                              "Handful of wealthy private donors", 
                                              "Government grants")),
         relationship = factor(relationship, levels = c("Friendly", "Criticized", 
                                                        "Under crackdown")))

org_table <- organizations %>% 
  dummy_columns(select_columns = organization_columns,
                remove_selected_columns = TRUE) %>% 
  pivot_longer(cols = -org_id, names_to = "name", ) %>% 
  pivot_wider(names_from = org_id, values_from = value) %>% 
  separate(name, into = c("attribute", "option"), sep = "_") %>% 
  filter(!(option %in% c("Emergency response", "No", "Small private donations", "Friendly")))
```

```{r possible-personas}
persona_columns <- c("national.news", "international.news", "medium.follow.tv", 
                     "medium.follow.print", "medium.follow.online", "medium.follow.social", 
                     "medium.follow.radio", "medium.follow.email", "medium.follow.app", 
                     "follow.govt", "travel", "ideology", "trust.institutions", 
                     "should.be.charitable", "religious.attendance", "religion.importance", 
                     "religion", "trust.charity.importance", "trust.charities", 
                     "donation.frequency", "donated.last.year", "volunteered", 
                     "volunteer.frequency", "history.activism.personal", "history.activism.family",
                     "membership.church", "membership.sport", "membership.art", "membership.union", 
                     "membership.party", "membership.environment", "membership.professional", 
                     "membership.charitable", "membership.consumer", "membership.other", 
                     "gender", "marital", "education", "income", "race", "age")

persona_demographics <- expand_grid(
  income = c("Less than median", "More than median"),
  education = c("High school graduate", "4 year degree"),
  religious.attendance = c("Rarely", "At least once a month")
) %>% 
  mutate(demographics_id = 1:n())

persona_politics <- tribble(
  ~ideology, ~national.news, ~international.news, ~travel,
  "Extremely liberal", "At least once a day",  "Always", "Yes",
  "Extremely conservative", "At least once a day", "Always", "Yes",
  "Extremely liberal", "Rarely", "Never", "No",
  "Extremely conservative", "Rarely", "Never", "No"
) %>% 
  mutate(politics_id = 1:n())

persona_social <- tibble(
  social_id = 1:2,
  trust.institutions = c("Complete trust", "No trust"),
  should.be.charitable = c("Strongly agree", "Strongly disagree"),
  trust.charities = c("Complete trust", "No trust"),
  volunteer.frequency = c("At least once a month", "Rarely"),
  donation.frequency = c("At least once a month", 
                         "More than once a month, less than once a year"),
  history.activism.personal = c("Involved", "Not involved"),
  membership.party = c("Active member", "Don't belong"),
  membership.charitable = c("Active member", "Don't belong")
)

persona_possibilities <- expand_grid(
  demographics_id = persona_demographics$demographics_id,
  politics_id = persona_politics$politics_id,
  social_id = persona_social$social_id
) %>% 
  left_join(persona_demographics, by = "demographics_id") %>% 
  left_join(persona_politics, by = "politics_id") %>% 
  left_join(persona_social, by = "social_id") %>% 
  select(-ends_with("_id")) %>% 
  mutate(persona_id = paste0("persona", 1:n()))

# Columns that should be held constant
# persona_columns %>% .[!(. %in% colnames(persona_possibilities))] %>% cat(sep = "\n")

personas <- persona_possibilities %>% 
  mutate(
    medium.follow.tv = "Follow",
    medium.follow.print = "Follow",
    medium.follow.online = "Don't follow",
    medium.follow.social = "Follow",
    medium.follow.radio = "Don't follow",
    medium.follow.email = "Don't follow",
    medium.follow.app = "Don't follow",
    follow.govt = "Often",
    religion.importance = "Important",
    religion = "Protestant",
    trust.charity.importance = "Somewhat important",
    donated.last.year = "$100-$499",
    volunteered = "No",
    history.activism.family = "Not involved",
    membership.church = "Don't belong",
    membership.sport = "Don't belong",
    membership.art = "Don't belong",
    membership.union = "Don't belong",
    membership.environment = "Don't belong",
    membership.professional = "Don't belong",
    membership.consumer = "Don't belong",
    membership.other = "Don't belong",
    gender = "Male",
    marital = "Married",
    race = "White",
    age = "Less than median"
  ) %>% 
  select(persona_id, all_of(persona_columns)) %>% 
  mutate(
    national.news = factor(national.news, levels = c("Rarely", "Once a week", "At least once a day")),
    international.news = factor(international.news, levels = c("Never", "Sometimes", "Always")),
    medium.follow.tv = factor(medium.follow.tv, levels = c("Don't follow", "Follow")),
    medium.follow.print = factor(medium.follow.print, levels = c("Don't follow", "Follow")),
    medium.follow.online = factor(medium.follow.online, levels = c("Don't follow", "Follow")),
    medium.follow.social = factor(medium.follow.social, levels = c("Don't follow", "Follow")),
    medium.follow.radio = factor(medium.follow.radio, levels = c("Don't follow", "Follow")),
    medium.follow.email = factor(medium.follow.email, levels = c("Don't follow", "Follow")),
    medium.follow.app = factor(medium.follow.app, levels = c("Don't follow", "Follow")),
    follow.govt = factor(follow.govt, levels = c("Not often", "Often")),
    travel = factor(travel, levels = c("No", "Yes")),
    ideology = factor(ideology, 
                      levels = c("Extremely liberal", "Somewhat liberal", 
                                 "Slightly liberal", "Moderate", "Slightly conservative", 
                                 "Somewhat conservative", "Extremely conservative")),
    trust.institutions = factor(trust.institutions,
                                levels = c("No trust", "Very little trust", "Little trust", 
                                           "Neutral", "Some trust", "A lot of trust", "Complete trust")),
    should.be.charitable = factor(should.be.charitable,
                                  levels = c("Strongly disagree", "Disagree", "Somewhat disagree", 
                                             "Neutral", "Somewhat agree", "Agree", "Strongly agree")),
    religious.attendance = factor(religious.attendance,
                                  levels = c("Not sure", "Rarely", "At least once a month")),
    religion.importance = factor(religion.importance,
                                 levels = c("Not important", "Important")),
    religion = factor(religion, 
                      levels = c("Catholic", "Protestant", "Christian Orthodox", "Jewish", 
                                 "Muslim", "Sikh", "Hindu", "Buddhist", "Atheist", "Other")),
    trust.charity.importance = factor(trust.charity.importance,
                                      levels = c("Not important", "Very unimportant", 
                                                 "Somewhat unimportant", "Neutral", 
                                                 "Somewhat important", "Very important", "Essential")),
    trust.charities = factor(trust.charities,
                             levels = c("No trust", "Very little trust", "Little trust", 
                                        "Neutral", "Some trust", "A lot of trust", "Complete trust")),
    donation.frequency = factor(donation.frequency,
                                levels = c("More than once a month, less than once a year", "At least once a month")),
    donated.last.year = factor(donated.last.year,
                               levels = c("$1-$49", "$50-$99", "$100-$499", "$500-$999", 
                                          "$1000-$4,999", "$5000-$9,999", "$10,000+")),
    volunteered = factor(volunteered, levels = c("No", "Yes")),
    volunteer.frequency = factor(volunteer.frequency,
                                 levels = c("Haven't volunteered in past 12 months", "Rarely", 
                                            "More than once a month, less than once a year", 
                                            "At least once a month")),
    history.activism.personal = factor(history.activism.personal,
                                       levels = c("Not involved", "Involved")),
    history.activism.family = factor(history.activism.family,
                                     levels = c("Not involved", "Involved")),
    membership.church = factor(membership.church,
                               levels  = c("Don't belong", "Inactive member", "Active member")),
    membership.sport = factor(membership.sport,
                              levels = c("Don't belong", "Inactive member", "Active member")),
    membership.art = factor(membership.art,
                            levels = c("Don't belong", "Inactive member", "Active member")),
    membership.union = factor(membership.union,
                              levels = c("Don't belong", "Inactive member", "Active member")),
    membership.party = factor(membership.party,
                              levels = c("Don't belong", "Inactive member", "Active member")),
    membership.environment = factor(membership.environment,
                                    levels = c("Don't belong", "Inactive member", "Active member")),
    membership.professional = factor(membership.professional,
                                     levels  = c("Don't belong", "Inactive member", "Active member")),
    membership.charitable = factor(membership.charitable,
                                   levels  = c("Don't belong", "Inactive member", "Active member")),
    membership.consumer = factor(membership.consumer,
                                 levels  = c("Don't belong", "Inactive member", "Active member")),
    membership.other = factor(membership.other,
                              levels = c("Don't belong", "Inactive member", "Active member")),
    gender = factor(gender,
                    levels = c("Male", "Female", "Transgender", "Prefer not to say", "Other")),
    marital = factor(marital,
                     levels = c("Married", "Widowed", "Divorced", "Separated", "Never married")),
    education = factor(education,
                       levels = c("Less than high school", "High school graduate", "Some college", 
                                  "2 year degree", "4 year degree", "Graduate or professional degree", "Doctorate")),
    income = factor(income,
                    levels = c("Less than median", "More than median")),
    race = factor(race,
                  levels = c("White", "Black or African American", "American Indian or Alaska Native", 
                             "Asian", "Native Hawaiian or Pacific Islander", "Other")),
    age = factor(age,
                 levels = c("Less than median", "More than median"))
  )

persona_base_cases <- c(
  "national.news_Rarely",
  "international.news_Never",
  "follow.govt_Not often",
  "travel_No",
  "ideology_Extremely liberal",
  "trust.institutions_No trust",
  "should.be.charitable_Strongly disagree",
  "religious.attendance_Not sure",
  "religion.importance_Not important",
  "religion_Catholic",
  "trust.charity.importance_Not important",
  "trust.charities_No trust",
  "donation.frequency_More than once a month, less than once a year",
  "donated.last.year_$1-$49",
  "volunteered_No",
  "volunteer.frequency_Haven't volunteered in past 12 months",
  "history.activism.personal_Not involved",
  "history.activism.family_Not involved",
  "gender_Male",
  "marital_Married",
  "education_Less than high school",
  "income_Less than median",
  "age_Less than median"
)

persona_table <- personas %>% 
  dummy_columns(select_columns = persona_columns,
                remove_selected_columns = TRUE) %>% 
  pivot_longer(cols = -persona_id, names_to = "name", ) %>% 
  pivot_wider(names_from = persona_id, values_from = value) %>% 
  # Get rid of base cases
  filter(!(name %in% persona_base_cases)) %>% 
  filter(!str_detect(name, "Don't follow"),
         !str_detect(name, "Don't belong")) %>% 
  separate(name, into = c("attribute", "option"), sep = "_") %>% 
  # Add intercept
  add_row(attribute = "Intercept", option = "Intercept", .before = 1) %>% 
  mutate(across(everything(), ~replace_na(., 1)))
```

```{r predicted-market-shares}
predicted_betas <- persona_table %>% 
  summarize(across(starts_with("persona"), ~as.matrix(gammas) %*% as.matrix(.)))

expected_utilities <- exp(t(org_table[,3:ncol(org_table)]) %*% 
                            as.matrix(predicted_betas[,1:ncol(predicted_betas)])) %>% 
  as_tibble(rownames = "org")

prop_expected_utilities <- expected_utilities %>% 
  mutate(across(starts_with("persona"), ~. / sum(.)))
```

```{r finalize-data}
org_details <- organizations %>% 
  mutate(organization = str_replace(org_id, "org", "Org "),
         funding = fct_recode(funding, 
                              "Mostly funded by small donors" = "Small private donations",
                              "Mostly funded by government grants" = "Government grants"),
         relationship = fct_rev(relationship)) %>%
  select(org_id, organization, org_issue = issue.area, 
         org_funding = funding, org_relationship = relationship)

persona_details <- personas %>% 
  mutate(persona_income = fct_recode(income, 
                                     "Lower income" = "Less than median", 
                                     "Higher income" = "More than median"),
         persona_education = fct_recode(education, "College graduate" = "4 year degree"),
         persona_religion = fct_recode(religious.attendance, 
                                       "Rarely attends religious services" = "Rarely",
                                       "Attends at least monthly" = "At least once a month"),
         persona_ideology = fct_recode(ideology, 
                                       "Conservative" = "Extremely conservative",
                                       "Liberal" = "Extremely liberal"),
         persona_experience = ifelse(travel == "Yes", 
                                     "Follows the news; has travelled abroad", 
                                     "Doesn't follow news; has not travelled abroad"),
         persona_trust = ifelse(trust.charities == "Complete trust", 
                                "More trusting; donates and volunteers often", 
                                "Less trusting; donates and volunteers less often")) %>% 
  mutate(persona = str_replace(persona_id, "persona", "Persona ")) %>% 
  select(persona, starts_with("persona"))

sim_clean <- prop_expected_utilities %>% 
  pivot_longer(cols = -org, names_to = "persona_id", values_to = "share") %>% 
  left_join(org_details, by = c("org" = "org_id")) %>% 
  left_join(persona_details, by = "persona_id")
```

```{r save-clean-data}
write_rds(sim_excel_clean, here("data", "derived_data", "sim_excel_final.rds"))
write_rds(sim_clean, here("data", "derived_data", "sim_final.rds"))
```

>>>>

---
title: "Generate and clean simulated data"
author: "Suparna Chaudhry, Marc Dotson, and Andrew Heiss"
date: "Last run: `r format(Sys.time(), '%F')`"
output: 
  html_document:
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

# `targets` pipeline

Here's the general process for building and running this analysis. This is all done with [the magical **`targets`** package](https://docs.ropensci.org/targets/), which orchestrates all the dependencies automatically.

```{r show-targets-pipeline, echo=FALSE}
withr::with_dir(here::here(), {
  targets::tar_glimpse()
})
```

# Actual code

All the simulation and data processing is handled with dataset-specific functions that live in `R/funs_data-generation.R`, which **`targets`** then runs as needed. For the sake of transparency, here's that code:

```{r, code=xfun::read_utf8(here::here("R", "funs_data-generation.R")), eval=FALSE, class.source="fold-show"}
```

### 2021-04-17 analysis/02_tables.Rmd
Use targets now!

---
title: "Tables"
author: "Suparna Chaudhry, Marc Dotson, and Andrew Heiss"
date: "Last run: `r format(Sys.time(), '%F')`"
output: 
  html_document:
    code_folding: hide
    pandoc_args:
      - "--default-image-extension=png"
editor_options: 
  chunk_output_type: console
---

```{r packages, warning=FALSE, message=FALSE, include=FALSE}
library(tidyverse)
library(pander)
library(magrittr)
library(glue)
library(scales)
library(janitor)
library(here)
```

```{r load-data}
sim_clean <- read_rds(here("data", "derived_data", "sim_final.rds"))
results <- read_rds(here("data", "raw_data", "final_data.rds"))

org_attributes <- tribble(
  ~`Issue area`, ~`Relationship with government`, ~`Funding`, ~`Funding sources`, ~`Organizational practices`, ~`Organization`,
  "Emergency response", "Friendly", "Small private donors", "Small private donors", "Financial transparency", "Amnesty International",
  "Environment", "Criticized", "Government grants", "Wealthy donors", "Accountability", "Greenpeace",
  "Human rights", "Crackdown", "", "Government grants", "", "Oxfam",
  "Refugee relief", "", "", "", "", "Red Cross"
)

persona_attributes <- tribble(
  ~`Demographics`, ~`Politics and public affairs`, ~`Social views`,
  "Higher income (> US median ($61,372)), high school graduate, frequent religious attendance", "Liberal (1), follows national and international news often, has traveled internationally", "High social trust: Trusts political institutions, trusts charities, thinks people should be more charitable, frequently volunteers, donates once a month, has a history of personal activism, is a member of an association",
  "Lower income (< US median), high school graduate, frequent religious attendance", "Conservative (7), follows news, has traveled", "Low social trust: Does not trust political institutions or charities, thinks people should be less charitable, does not volunteer or donate often, has no history of personal activism, is not a member of an association",
  "Higher income, college graduate, frequent religious attendance", "Liberal, does not follow news, has not traveled", "",
  "Lower income, college graduate, frequent religious attendance", "Conservative, does not follow news, has not traveled", "",
  "Higher income, high school graduate, rare religious attendance", "", "",
  "Lower income, high school graduate, rare religious attendance", "", "",
  "Higher income, college graduate, rare religious attendance", "", "",
  "Lower income, college graduate, rare religious attendance", "", ""
)
```

@@

```{r results="asis"}
org_attributes %>% 
  select(Organization, `Issue area`, `Organizational practices`, `Funding sources`, `Relationship with government`) %>% 
  pandoc.table.return(caption = 'Organization attributes varied in the experiment {#tbl:organization-attributes-full}',
                      justify = "lllll", split.tables = Inf) %T>%
  cat() %>%
  cat(file = here("analysis", "output", "tables", "tbl-organization-attributes-full.md"))
```

@@

```{r results="asis"}
org_attributes %>% 
  select(`Issue area`, `Relationship with government`, `Funding`) %>% 
  pandoc.table.return(caption = 'Organization attributes varied in the simulation, resulting in 24 hypothetical organizations {#tbl:organization-attributes}',
                      justify = "lll") %T>%
  cat() %>%
  cat(file = here("analysis", "output", "tables", "tbl-organization-attributes.md"))
```

@@

```{r results="asis"}
persona_attributes %>% 
  pandoc.table.return(caption = 'Individual attributes varied in the simulation, resulting in 64 persona profiles {#tbl:persona-attributes}',
                      justify = "lll", split.tables = Inf) %T>%
  cat() %>%
  cat(file = here("analysis", "output", "tables", "tbl-persona-attributes.md"))
```

@@

```{r results="asis"}
example_personas <- c("persona2", "persona63")

example_persona_details <- sim_clean %>%
  filter(persona_id %in% example_personas) %>% 
  select(starts_with("persona")) %>% 
  slice(1:2)

example_persona_details %>% 
  select(-persona_id) %>% 
  pivot_longer(cols = !persona) %>% 
  pivot_wider(names_from = "persona", values_from = "value") %>% 
  select(-name) %>% 
  pandoc.table(justify = "ll")
```

```{r results="asis"}
example_persona_results <- sim_clean %>% 
  filter(persona_id %in% example_personas) %>% 
  mutate(org_funding = str_to_sentence(str_remove(org_funding, "Mostly funded by "))) %>% 
  mutate(org_clean = glue("{organization}: {org_issue}, {org_funding}, {org_relationship}")) %>% 
  mutate(persona_desc = recode(
    persona_id,
    "persona2" = "Lower income high school graduate who rarely attends religious services; liberal who reads and travels; doesn't trust or donate",
    "persona63" = "Higher income college graduate who attends religious services; conservative who doesn't read or travel; trusts and donates")
  ) %>%
  mutate(persona_clean = glue("{persona}: {persona_desc}")) %>% 
  select(persona_clean, share, org_clean) %>% 
  pivot_wider(names_from = "persona_clean", values_from = "share") %>% 
  adorn_totals(where = "row", name = "**Total**")

@@

example_persona_results_small %>% 
  pandoc.table.return(caption = 'Sample simulation output {#tbl:sim-output}',
                      justify = "lcc", split.tables = Inf) %T>%
  cat() %>%
  cat(file = here("analysis", "output", "tables", "tbl-sim-output.md"))
```

@@

```{r}
vars_to_summarize <- tribble(
  ~category, ~variable, ~clean_name,
  "Demographics", "Q5.12", "Gender",
  "Demographics", "Q5.17", "Age",
  "Demographics", "Q5.13", "Marital status",
  "Demographics", "Q5.14", "Education",
  "Demographics", "Q5.15", "Income",
  "Attitudes toward charity", "Q2.5", "Frequency of donating to charity",
  "Attitudes toward charity", "Q2.6", "Amount of donations to charity last year",
  "Attitudes toward charity", "Q2.7_f", "Importance of trusting charities",
  "Attitudes toward charity", "Q2.8_f", "Level of trust in charities",
  "Attitudes toward charity", "Q2.10", "Frequency of volunteering",
  "Politics, ideology, and religion", "Q2.1", "Frequency of following national news",
  "Politics, ideology, and religion", "Q5.7", "Traveled to a developing country",
  "Politics, ideology, and religion", "Q5.1", "Voted in last election",
  "Politics, ideology, and religion", "Q5.6_f", "Trust in political institutions and the state",
  "Politics, ideology, and religion", "Q5.2_f", "Political ideology",
  "Politics, ideology, and religion", "Q5.4", "Involvement in activist causes",
  "Politics, ideology, and religion", "Q5.8", "Frequency of attending religious services",
  "Politics, ideology, and religion", "Q5.9", "Importance of religion"
)

summarize_factor <- function(x) {
  output <- table(x) %>% 
    as_tibble() %>% 
    magrittr::set_colnames(., c("level", "count")) %>% 
    mutate(level = factor(level, levels = levels(x))) %>%
    mutate(prop = count / sum(count),
           nice_prop = scales::percent(prop))

  return(list(output))
}

participant_summary <- results %>% 
  select(one_of(vars_to_summarize$variable)) %>% 
  summarize_all(summarize_factor) %>% 
  pivot_longer(cols = everything(), names_to = "variable", values_to = "details") %>% 
  left_join(vars_to_summarize, by = "variable") %>% 
  unnest(details) %>% 
  mutate(level = as.character(level)) %>% 
  mutate(level = case_when(
    variable == "Q2.7_f" & level == "1" ~ "1 (not important)",
    variable == "Q2.7_f" & level == "7" ~ "7 (important)",
    variable == "Q2.8_f" & level == "1" ~ "1 (no trust)",
    variable == "Q2.8_f" & level == "7" ~ "7 (complete trust)",
    variable == "Q5.6_f" & level == "1" ~ "1 (no trust)",
    variable == "Q5.6_f" & level == "7" ~ "7 (complete trust)",
    variable == "Q5.2_f" & level == "1" ~ "1 (extremely liberal)",
    variable == "Q5.2_f" & level == "7" ~ "7 (extremely conservative)",
    variable == "Q5.15" & level == "Less than median" ~ "Less than 2017 national median ($61,372)",
    variable == "Q5.17" & level == "Less than median" ~ "Less than 2017 national median (36)",
    TRUE ~ level
  )) %>% 
  mutate(clean_name_shrunk = ifelse(clean_name == lag(clean_name), "", clean_name),
         clean_name_shrunk = ifelse(is.na(clean_name_shrunk), 
                                    clean_name[1], 
                                    clean_name_shrunk),
         category_shrunk = ifelse(category == lag(category), "", category),
         category_shrunk = ifelse(is.na(category_shrunk), 
                                    category[1], 
                                    category_shrunk))
```

```{r results="asis"}
participant_summary %>% 
  select("Category" = category_shrunk, "Question" = clean_name_shrunk, 
         "Response" = level, "N" = count, "%" = nice_prop) %>% 
  pandoc.table.return(caption = 'Summary of individual respondent characteristics {#tbl:sample-details}',
                      justify = "lllcc", split.tables = Inf) %T>%
  cat() %>%
  cat(file = here("analysis", "output", "tables", "tbl-sample-details.md"))
```

>>>>

---
title: "Tables"
author: "Suparna Chaudhry, Marc Dotson, and Andrew Heiss"
date: "Last run: `r format(Sys.time(), '%F')`"
output: 
  html_document:
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.retina = 3,
                      tidy.opts = list(width.cutoff = 120),  # For code
                      options(width = 90),  # For output
                      fig.asp = 0.618, fig.width = 7, 
                      fig.align = "center", out.width = "85%")

options(dplyr.summarise.inform = FALSE,
        knitr.kable.NA = "")
```

```{r load-libraries-data, message=FALSE, warning=FALSE}
library(tidyverse)
library(targets)
library(kableExtra)
library(glue)
library(scales)
library(janitor)
library(here)

# Generated via random.org
set.seed(8316)

# Load data
# Need to use this withr thing because tar_read() and tar_load() need to see the
# _targets folder in the current directory, but this .Rmd file is in a subfolder
withr::with_dir(here::here(), {
  tar_load(personas)
  tar_load(orgs)
  tar_load(sim_final)
  tar_load(survey_results)
  tar_load(participant_summary)
})
```

@@

```{r organization-attributes-full}
orgs$org_attributes %>% 
  select(Organization, `Issue area`, `Organizational practices`, `Funding sources`, `Relationship with government`) %>% 
  kbl(align = "lllll",
      caption = "Organization attributes varied in the experiment") %>% 
  kable_styling()
```

@@

```{r organization-attributes}
orgs$org_attributes %>% 
  select(`Issue area`, `Relationship with government`, `Funding`) %>% 
  kbl(align = "lll",
      caption = "Organization attributes varied in the simulation, resulting in 24 hypothetical organizations") %>% 
  kable_styling()
```

@@

```{r persona-attributes}
personas$persona_attributes %>% 
  kbl(align = "lll",
      caption = "Individual attributes varied in the simulation, resulting in 64 persona profiles") %>% 
  kable_styling()
```

@@

```{r example-personas}
example_personas <- c("persona2", "persona63")

example_persona_details <- sim_final %>%
  filter(persona_id %in% example_personas) %>% 
  select(starts_with("persona")) %>% 
  slice(1:2)

example_persona_details %>% 
  select(-persona_id) %>% 
  pivot_longer(cols = !persona) %>% 
  pivot_wider(names_from = "persona", values_from = "value") %>% 
  select(-name) %>% 
  kbl(align = "ll",
      caption = "Example personas") %>% 
  kable_styling()
```

```{r sim-output}
example_persona_results <- sim_final %>% 
  filter(persona_id %in% example_personas) %>% 
  mutate(org_funding = str_to_sentence(str_remove(org_funding, "Mostly funded by "))) %>% 
  mutate(org_clean = glue("{organization}: {org_issue}, {org_funding}, {org_relationship}")) %>% 
  mutate(persona_desc = recode(
    persona_id,
    "persona2" = "Lower income high school graduate who rarely attends religious services; liberal who reads and travels; doesn't trust or donate",
    "persona63" = "Higher income college graduate who attends religious services; conservative who doesn't read or travel; trusts and donates")
  ) %>%
  mutate(persona_clean = glue("{persona}: {persona_desc}")) %>% 
  select(persona_clean, share, org_clean) %>% 
  pivot_wider(names_from = "persona_clean", values_from = "share") %>% 
  adorn_totals(where = "row", name = "Total")

@@

example_persona_results_small %>% 
  mutate(Organization = text_spec(Organization, bold = Organization == "Total")) %>% 
  kbl(align = "lcc",
      caption = "Sample simulation output",
      escape = FALSE) %>% 
  kable_styling()
```

@@

```{r sample-details}
participant_summary %>% 
  select(Question = clean_name,
         Response = level,
         N = count,
         `%` = nice_prop) %>% 
  kbl(align = "lllcc",
      caption = "Summary of individual respondent characteristics") %>% 
  pack_rows(index = table(fct_inorder(participant_summary$category))) %>%
  collapse_rows(columns = 1, valign = "top") %>% 
  kable_styling()
```
